Type Refinements for the Working Class

### 2016-03-15 paper.tex
fix typos

Given a family of refinements (i.e. a functional refinement)
$\FRefines{\Upsilon}{x:\phi}{\psi}{\tau}$ such that
$\Refines{\Upsilon}{\phi}{\sigma}$, including the family intersection, the
dependent intersection, the family union, and the set comprehension.

@@

In this section we generalize Howe's notion of lazy computation
system~\cite{howe:1989} to the multi-sorted, symbol-parameterized setting. An
\emph{lazy computation language} is an abt signature
$\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ along with a distinguished
arity-indexed family of copresheaves
$\HypJ{\Of{\CanOperators_a}{\Sets^\SCtx}}{\Member{a}{\Arities}}$ of
\emph{canonical} operators such that
$\IsSubsetEq{\CanOperators_a}{\Operators_a}$ for each arity $a$.

@@

\begin{thm}
  Nominal independence is an idempotent comonadic modality on refinements.
\end{thm}
\begin{proof}
  The demonstration is essentially analogous to the one for independence in
  Theorem~\ref{thm:independence-comonadic}.
\end{proof}

>>>>

Given a family of refinements (i.e. a functional refinement)
$\FRefines{\Upsilon}{x:\phi}{\psi}{\tau}$ such that
$\Refines{\Upsilon}{\phi}{\sigma}$, we may construct a number of new refinement
connectives, including the family intersection, the dependent intersection, the
family union, and the set comprehension.

@@

In this section we adapt Howe's notion of lazy computation
system~\cite{howe:1989} to the multi-sorted, symbol-parameterized setting. An
\emph{lazy computation language} is an abt signature
$\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ along with a distinguished
arity-indexed family of copresheaves
$\HypJ{\Of{\CanOperators_a}{\Sets^\SCtx}}{\Member{a}{\Arities}}$ of
\emph{canonical} operators such that
$\IsSubsetEq{\CanOperators_a}{\Operators_a}$ for each arity $a$.

@@

\begin{thm}
  Nominal necessity is an idempotent comonadic modality on refinements.
\end{thm}
\begin{proof}
  The demonstration is essentially analogous to the one for independence in
  Theorem~\ref{thm:independence-comonadic}.
\end{proof}
